Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run the
  original version of Optician (\OpticianRuntime{}) and \QOpt{}
  (\QREOptician{}) on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  and then extending the synthesis specification to include QREs.
  (In other words, we restored them to their original state, added QREs,
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

To assess the performance of QRE synthesis, we are interested in two
different questions.  First, how does the performance of \QOpt{} 
compare to the performance of the original
version of Optician on benchmarks that do not require QREs?  The
answer to this question tells us how much overhead we have introduced
by adopting the more general mechanism.  
Figure~\ref{fig:times}(a) shows that \QOpt{} was able to synthesize
all of the Optician benchmarks at a speed competative with the old
version. 
There is a small amount
of additional overhead introduced by QREs in calculating the $W$ and
$K$ functions, resulting in a slight decrease in performance.

@@

\section{Related Work}
\label{relwork}
This paper builds on the work of Foster et al~\cite{quotientlenses} who
introduced the theory of quotient lenses and implemented quotient lenses as a
refinement of the bidirectional string processing language
Boomerang~\cite{boomerang}. As we mentioned in
Section\cref{subsec:well-formed-qres}, all our QRE combinators can be expressed
using just the {\em normalize} combinator, which is one of the canonizer
primitives that Boomerang already supports. Also, all our QRE lens combinators
are already supported in Boomerang. Consequently Boomerang quotient lenses are
at least as expressive as our language of QRE lenses.

>>>>

\begin{figure}[t]
\centering
\begin{subfigure}[b]{.49\textwidth}
\centering
\includegraphics{generated-graphs/times_opt}
\caption{}
\label{subfig:lenssize}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}
\includegraphics{generated-graphs/times_new.eps}
\caption{}
\label{subfig:examplesused}
\end{subfigure}
\caption{Runtimes measurements. In (a), we run Optician and \QOpt{}
  on the Optician benchmarks.  We find that there is only a negligible
  performance overhead incurred by using QREs. 
  In (b), we run \QOpt{} on the 10 Optician benchmarks
  previously edited to make them bijective, after removing those edits
  and then extending the synthesis specification to include QREs.
  (In other words, we restored them to their original state, added QREs,
  and then ran \QOpt{}). 
  We find that \QOpt{} is able to
  synthesize all quotient lenses in under 10 seconds, and typically finishes in
  under 5 seconds.}
\label{fig:times}
\end{figure}

To assess the performance of QRE synthesis, we are interested in two different
questions. First, how does the performance of \QOpt{} compare to the performance
of Optician on benchmarks that do not require QREs? The answer to this question
tells us how much overhead we have introduced by adopting the more general
mechanism. Figure~\ref{fig:times}(a) shows that \QOpt{} was able to synthesize
all of the Optician benchmarks at a speed competative with the old version.
There is a small amount of additional overhead introduced by QREs in calculating
the $W$ and $K$ functions, resulting in a slight decrease in performance.

@@

\section{Related Work}
\label{relwork}
This paper builds on the work of Foster et al~\cite{quotientlenses} who
introduced the theory of quotient lenses and implemented quotient lenses as a
refinement of the bidirectional string processing language
Boomerang~\cite{boomerang}. As we mentioned in
Section~\ref{subsec:well-formed-qres}, all our QRE combinators can be expressed
using just the {\em normalize} combinator, which is one of the canonizer
primitives that Boomerang already supports. Also, all our QRE lens combinators
are already supported in Boomerang. Consequently Boomerang quotient lenses are
at least as expressive as our language of QRE lenses.
